You all know the old song:


\hskip 1cm On the first day of Christmas my true love gave to me a partridge in a pear tree.

\hskip 1cm On the second day of Christmas my true love gave to me two turtle doves and a partridge in a pear tree.

\hskip 1cm On the third day of Christmas my true love gave to me three French hens, two turtle doves and a partridge in a pear tree.

\hskip 1cm On the fourth day of Christmas my true love gave to me four calling birds, three French hens, two turtle doves and a partridge in a pear tree.

\hskip 1cm On the fifth day of Christmas my true love gave to me five golden rings, four calling birds, three French hens, two turtle doves and a partridge in a pear tree.

\hskip 1cm On the sixth day of Christmas my true love gave to me six geese a-laying, five golden rings, four calling birds, three French hens, two turtle doves and a partridge in a pear tree.

\hskip 1cm On the seventh day of Christmas my true love gave to me seven swans a-swimming, six geese a-laying, five golden rings, four calling birds, three French hens, two turtle doves and a partridge in a pear tree.

\hskip 1cm On the eighth day of Christmas my true love gave to me eight maids a-milking, seven swans a-swimming, six geese a-laying, five golden rings, four calling birds, three French hens, two turtle doves and a partridge in a pear tree.

\hskip 1cm On the ninth day of Christmas my true love gave to me nine ladies dancing, eight maids a-milking, seven swans a-swimming, six geese a-laying, five golden rings, four calling birds, three French hens, two turtle doves and a partridge in a pear tree.

\hskip 1cm On the tenth day of Christmas my true love gave to me ten lords a-leaping, nine ladies dancing, eight maids a-milking, seven swans a-swimming, six geese a-laying, five golden rings, four calling birds, three French hens, two turtle doves and a partridge in a pear tree.

\hskip 1cm On the eleventh day of Christmas my true love gave to me eleven pipers piping, ten lords a-leaping, nine ladies dancing, eight maids a-milking, seven swans a-swimming, six geese a-laying, five golden rings, four calling birds, three French hens, two turtle doves and a partridge in a pear tree.

\hskip 1cm On the twelfth day of Christmas my true love gave to me twelve drummers drumming, eleven pipers piping, ten lords a-leaping, nine ladies dancing, eight maids a-milking, seven swans a-swimming, six geese a-laying, five golden rings, four calling birds, three French hens, two turtle doves and a partridge in a pear tree.

Your task is to write a program that prints the words of the song, as economically as possible. When you are finished, you are welcome to read or run a suggested solution, or to post your own solution or discuss the exercise in the comments below.


\bye